---
title: "Curriculum Vitae"
---

## Education
```{r}
#| echo: false
knitr::kable(
  data.frame(
    Degree = c("MSc Animal Science", "BSc Agriculture"),
    Institution = c("São Paulo State University", "Federal University of Santa Catarina"),
    Period = c("2023-2025", "2017-2022"),
    GPA = c("CAPES Scholarship", "8.74/10")
  )
)
```


## Professional Experience

::: {.timeline}

**2025-Present**  
**Research Assistant**  
São Paulo State University  
- Training teams on experimental procedures  
- Statistical analysis planning  
- Technical report writing  

**2024**  
**Visiting Research Student**  
University of British Columbia  
- Animal welfare research collaboration  
- Presented findings at international seminars  

**2023-2024**  
**Herdsperson**  
EMBRAPA Pecuária Sudeste  
- Managed dairy calf health protocols  
- Implemented vaccination programs  

**2023-2025**  
**Graduate Researcher**  
São Paulo State University  
- Coordinated international dairy cattle welfare projects  
- Developed patents and scientific papers  

**2023**  
**Teaching Intern**  
São Paulo State University  
- Taught "Dairy Cattle" for veterinary students  

**2022**  
**Farm Labourer**  
Estância Santa Bárbara  
- Managed operations for 11,000-head sheep farm  

**2019-2022**  
**Research Assistant**  
Federal University of Santa Catarina (LETA)  
- Led dairy cattle behavior studies  
- Developed outreach materials  

**2018**  
**Teaching Assistant**  
Federal University of Santa Catarina  
- Physics instruction for agriculture students  

**2017-2018**  
**Search Engine Evaluator**  
Lionbridge  
- Improved search algorithm quality  

:::


## Skills Matrix
```{r}
#| echo: false
#| fig-width: 8
#| fig-height: 3
library(ggplot2)
skills <- data.frame(
  skill = c("R Programming", "GLMMs", "Data Viz", "Quarto", "Animal Science", "Project Mgmt"),
  level = c(95, 90, 85, 90, 95, 80)
)

ggplot(skills, aes(x = reorder(skill, -level), y = level)) +
  geom_col(fill = "#2E86AB", width = 0.7) +
  geom_text(aes(label = paste0(level, "%")), vjust = -0.5) +
  ylim(0, 100) +
  labs(x = NULL, y = "Proficiency (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

